SDM\_the\_search\_for\_powers\_of\_2\_everywhere

### 2018-04-19 Chapters/sdm-autocorrelation.tex
SDM Autocorrelation.

$$
\frac{1}{2^a} \sum_{k=0}^{b} \binom{a}{k} = \Phi \left( \frac{b-a/2}{\sqrt{a}/2} \right) = \Phi \left( \frac{2b-a}{\sqrt{a}} \right)$
$$

@@

$$
\sum_{k=0}^{b} \binom{a}{k} = 2^a \Phi \left( \frac{2b-a}{\sqrt{a}} \right)$
$$

@@

In Figure \ref{fig:sdm-10kbits-figure-7-3}, with $n=10,000$ and $r=4,845$, we can notice that the autocorrelation has vanished as predicted by Theorem \ref{thm:sdm-autocorrelation-convergence}. In fact, in this case, $P(x_i = y_i | d(x, y) \le r) = 0.5039895557907589$.

@@

  \caption{The same setup as in Figure \ref{fig:sdm-10000w-table-7-2}, but for $n=10,000$. It shows that the interference has gone away when $n$ is sufficiently large.}
  \label{fig:sdm-10kbits-figure-7-3}
\end{figure}

>>>>

$$
\frac{1}{2^a} \sum_{k=0}^{b} \binom{a}{k} = \Phi \left( \frac{b-a/2}{\sqrt{a}/2} \right) = \Phi \left( \frac{2b-a}{\sqrt{a}} \right)
$$

@@

$$
\sum_{k=0}^{b} \binom{a}{k} = 2^a \Phi \left( \frac{2b-a}{\sqrt{a}} \right)
$$

@@

In Figure \ref{fig:sdm-10kbits-figure-7-3}, with $n=10,000$ and $r=4,845$, we can notice that the autocorrelation has reduced significantly as predicted by Theorem \ref{thm:sdm-autocorrelation-convergence}. In fact, in this case, using Lemma \ref{thm:sdm-T1-n-large}, $P(x_i = y_i | d(x, y) \le r) = 0.5168761116022098$.

@@

  \caption{The same setup as in Figure \ref{fig:sdm-10000w-table-7-2}, but for $n=10,000$. It shows that the interference has almost gone away when $n$ is sufficiently large.}
  \label{fig:sdm-10kbits-figure-7-3}
\end{figure}
